Biogears in Anesthesia Screen Based Simulation

### 2016-02-22 paper_working_on/paper.tex
extract the data from cae experiment and add jpg to paper

\subsection{oxygen desaturation Scenarios}

@@

As we can see on the graphs, both patients' oxygen saturation drops as they stopped breathing and once we restore the air supply, they recovered from it in 25 seconds. And there actually isn't difference in how long it will take them to recover from the deficiency. It shows that Biogears is currently not capable to simulate this complex yet delicate recovery scenarios.

>>>>

\subsection{Oxygen Desaturation Scenarios}

@@

As we can see on the graphs, both patients' oxygen saturation drops as they stopped breathing and once we restore the air supply, they recovered from it in 25 seconds. And there actually isn't difference in how long it will take them to recover from the deficiency. It shows that Biogears is currently not capable of simulating this complex yet delicate recovery scenarios.

\subsection{Tests for Common Drugs}

\subsubsection{Succinycholine Simulation}

Succinycholine is a drug that could trigger short-period muscle relaxation and therefore used as an approach to induce short-period paralysis. In the discipline of anesthesia, it is used widely for emergency medicine and trauma care due to its fast-acting and short-duration nature. Therefore, adjusting its dosage to multiple scenarios is important for those who wish to practice their knowledge and become anaesthetist in the future.

In Biogears, we set up the Succinycholine's dosage to be 5 mg as suggested by Dr. Mchvor. We simulated the scenario for  
more than 900 seconds cause it takes time for patient to recover from paralysis.
\begin{figure}[!htb]\centering
   \begin{minipage}{0.49\textwidth}
     \frame{\includegraphics[width=5cm]{Succinylcholine_HeartRate_vs_Time.jpg}}
     \caption{Heart Rate changes}
     \label{fig:given 5 mg Succinylcholine}

   \end{minipage}
   \begin {minipage}{0.49\textwidth}
     \frame{\includegraphics[width=5cm]{Succinylcholine_OxygenSaturation_vs_Time.jpg}}
     \caption{Oxygen Saturation changes}
     \label{fig:given 5 mg Succinylcholine}
   \end{minipage}
\end{figure}

\begin{figure}[!htb]\centering
   \begin{minipage}{0.49\textwidth}
     \frame{\includegraphics[width=5cm]{Succinylcholine_ArterialPressure_vs_Time.jpg}}
     \caption{Blood Pressure changes}
     \label{fig:given 5 mg Succinylcholine}

   \end{minipage}
   \begin {minipage}{0.49\textwidth}
     \frame{\includegraphics[width=5cm]{Succinylcholine_RespirationRate_vs_Time.jpg}}
     \caption{Respiration Rate changes}
     \label{fig:given 5 mg Succinylcholine}
   \end{minipage}
\end{figure}

In CAE, we set up the Succinycholine's dosage to be 77mg cause Muse only provides options for injection corresponding to the patient weight. We simulated the scenario for more than

When observing the result graphs, we could see that patient stopped breathing for nearly 4 minutes.

\subsubsection{Rocuronium 50 mg Simulation}

\subsubsection{Propofol 200 mg Simulation}

\subsubsection{Morphine 40 mg Simulation}

\subsubsection{Fentanyl 500 ug Simulation}
